Web Page Visualization Code

### 2024-08-25 Scripts - Data Cleaning and Visuals/_Webpage Visualizations Code.Rmd
fixed directories again

plt.figure(figsize=(10, 6))
plt.imshow(wordcloud_positive, interpolation='bilinear')
plt.axis('off')
plt.title('Top Words in Positive Sentiment Comments')
plt.tight_layout()
0_output_path = os.path.join(output_directory, "images and tables/word_cloud_positive_sentiment.png"))
plt.savefig(0_output_path)
plt.show()

>>>>

plt.figure(figsize=(10, 6))
plt.imshow(wordcloud_positive, interpolation='bilinear')
plt.axis('off')
plt.title('Top Words in Positive Sentiment Comments')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/word_cloud_positive_sentiment.png"))
plt.savefig(0_output_path)
plt.show()
